\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-15 paper.qmd
Updated Figure 2

scurve_proj1_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696")

@@

scurve_proj2_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696")

@@

scurve_proj3_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696")

@@

```{r}
#| label: fig-scurve-proj
#| fig-cap: "Three views of the true model (grey points and lines) in $2\text{-}D$ projections from $7\text{-}D$, for the S-curve data (purple points). The data is spread along the S shape, and does not vary much from this curve. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/I5GL23vLiw0>)."

>>>>

scurve_proj1_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696")

@@

scurve_proj2_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696")

@@

scurve_proj3_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696")

@@

```{r}
#| label: fig-scurve-true-sc
#| fig-cap: "Three views of the true model (grey points and lines) in $2\\text{-}D$ projections from $7\\text{-}D$, for the S-curve data (purple points). The data is spread along the S shape, and does not vary much from this curve. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/I5GL23vLiw0>)."

### 2024-08-15 paper.tex
Updated Figure 2

\begin{minipage}{0.33\linewidth}
\begin{center}
\includegraphics[width=1.5625in,height=\textheight]{figures/scurve/sc_true_1.png}
\end{center}
\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\begin{center}
\includegraphics[width=1.5625in,height=\textheight]{figures/scurve/sc_true_2.png}
\end{center}
\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\begin{center}
\includegraphics[width=1.5625in,height=\textheight]{figures/scurve/sc_true_3.png}
\end{center}
\end{minipage}%

>>>>

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-scurve-true-sc-1.pdf}
